---
title: "Cape_Moreton"
author: "P. Melloy"
date: "23/02/2021"
output: html_document
---

```{r libraries}
#install.packages("bomrang")
library(bomrang)
library(dplyr)
library(ggplot2)
```

```{r find_station}
approx_cape_moreton_latlon <- c(-27.0314, 153.454)

# find stations near the latitude and logitude above
stations <- sweep_for_stations(latlon = c(-27.0314, 153.454))

head(stations)
```

```{r get_Cape_Moreton_data}
C_moreton_min <-
   get_historical(latlon = unlist(stations[1, c("lat", "lon")]),type = c("min"))

C_moreton_max <-
   get_historical(latlon = unlist(stations[1, c("lat", "lon")]),type = c("max"))

head(C_moreton_min)
```

Let's describe the data a little:  
 - The earliest year for minimum temperature observations was `r min(C_moreton_min$year)`  
 - The latest year for minimum temperature observations was `r max(C_moreton_min$year)`  
 - missing years `r any(!(min(C_moreton_min$year):max(C_moreton_min$year) %in% unique(C_moreton_min$year)))`  
 - The earliest year for minimum temperature observations was `r min(C_moreton_max$year)`  
 - The latest year for minimum temperature observations was `r max(C_moreton_max$year)`  
 - missing years `r any(!(min(C_moreton_max$year):max(C_moreton_max$year) %in% unique(C_moreton_max$year)))`  
 -


```{r data_summary}
max(C_moreton_min$year) -
min(C_moreton_min$year)
```

Plot boxplots of temperature minimums over the 111 years of observation
```{r min_boxplot, fig.width= 4, fig.height=10}
C_moreton_min %>%
   filter(year != 2021)%>% # remove 2021 due to incomplete yearly data
   ggplot(aes(x = factor(year), y = min_temperature))+
   geom_boxplot()+
   geom_hline(yintercept = median(C_moreton_min$min_temperature, na.rm = TRUE))+
   coord_flip() +
     scale_x_discrete(breaks = seq(from = min(C_moreton_min$year),
                                 to = max(C_moreton_min$year),
                                 by = 5),
                    labels = seq(from = min(C_moreton_min$year),
                                 to = max(C_moreton_min$year),
                                 by = 5))
```



Plot boxplots of temperature maximums over the 111 years of observation
```{r max_boxplot, fig.width= 4, fig.height=10}
C_moreton_max %>%
   filter(year != 2021)%>% # remove 2021 due to incomplete yearly data
   ggplot(aes(x = factor(year), y = max_temperature))+
   geom_boxplot()+
   geom_hline(yintercept = median(C_moreton_max$max_temperature, na.rm = TRUE))+
   coord_flip() + 
   scale_x_discrete(breaks = seq(from = min(C_moreton_max$year),
                                 to = max(C_moreton_max$year),
                                 by = 5),
                    labels = seq(from = min(C_moreton_max$year),
                                 to = max(C_moreton_max$year),
                                 by = 5))
```

__NOTE: Early measurements such as between 1910 - 1916 were likely warmer due to measurements taken from non shaded thermometers__
(BOM early data)[http://www.bom.gov.au/climate/data/acorn-sat/#tabs=Early-data]

